\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{geometry}
\usepackage{multicol}

\geometry{
    left=1cm,right=1cm,top=2cm,bottom=2cm
}
\newcommand*\diff{\mathop{}\!\mathrm{d}}

\newtheorem{definition}{Определение}
\newtheorem{theorem}{Теорема}

\DeclareMathOperator{\sign}{sign}

\usepackage{hyperref}
\hypersetup{
    colorlinks, citecolor=black, filecolor=black, linkcolor=black, urlcolor=black
}

\title{Английский язык}
\author{Лисид Лаконский}
\date{October 2023}

\begin{document}
\raggedright

\maketitle

\tableofcontents
\pagebreak

\section{Практическое занятие — 14.10.2023}

\subsection{Reading 1}

\subsubsection{Exercise 1}

\textbf{Dicuss the following with your partner and choose the best answer:}

People talk a lot in the information technology business about "intellectual property rights". What are they?

\begin{enumerate}
    \item How do they apply to software technology?
    
    Intellectual property rights protect also software technologies.
    \item Why should you protect them?
    
    To protect my assets from theft.
    \item How do you protect them?
    
    I protect my software technologies with licenses.
\end{enumerate}

\subsubsection{Exercise 2}

\textbf{Match the words (1-10) with the definitions (A-J)}:

\begin{multicols}{2}
\begin{enumerate}
    \item patent — limited legal monopoly...
    \item copyright — legal monopoly that protects...
    \item digital rights — technology through which the owner...
    \item infringement — violation...
    \item plagiarism — stealing of words... 
    \item software license — permission to use a software...
    \item asset — something valuable...
    \item idea generation — the process of creating...
    \item innovation — the process of translating...
    \item ownership — the ultimate and exclusive right...
\end{enumerate}
\end{multicols}

\subsubsection{Exercise 3}

\textbf{Answer the following questions:}

\begin{enumerate}
    \item What are intellectual property (IP) rights?
    
    Intellectual property rights are rights of creator of some invention, design or something else to prevent others from using it, to negotiate payment in return for others using them. 
    \item What forms of IP do you know?
    
    There are four types of intellectual property rights: patents, copyrights, trade secret and trademarks.
    \item How do IP rights apply in software technology?
    
    Patents, copyrights, trade secrets protect the technology itself, trademarks protect the names or symbols used to distinguish a product in the marketplace.
    \item What can a patent protect?
    
    Patent can protect ideas, systems, methods, algorithms, and functions embodied in a software product: editing functions, user-interface features, compiling techniques, etc.
    \item What can copyrights protect?
    
    In the case of software, copyright law would protect the source and object code, as well as certain unique original elements of the user interface.
    \item Why do companies have trade secrets?

    Companies have trade secrets to have competitive advantage.
    \item What features of software can be protected as trade secrets?
    
    Code and the ideas and concepts reflected in it can be protected as trade secrets.
\end{enumerate}

\subsubsection{Exercise 4}

\textbf{Match paragraph (1–7) with the correct heading (A-G)}

\begin{multicols}{2}
\begin{enumerate}
    \item Paragraph 1 — Ideas and knowledge
    \item Paragraph 2 — Intellectual property rights
    \item Paragraph 3 — Patent
    \item Paragraph 4 — Software patents
    \item Paragraph 5 — Copyrights protection
    \item Paragraph 6 — Exclusive right of a copyright owner
    \item Paragraph 7 — Trade secrets
\end{enumerate}
\end{multicols}

\subsubsection{Exercise 5}

\textbf{Read the text againi and decide whether these stateents are true, false, or information is not available}

\begin{enumerate}
    \item 
\end{enumerate}

\subsection{Домашнее задание}

\begin{enumerate}
    \item Подготовить презентацию на 5-7 минут про какого-либо russian scientist.
\end{enumerate}

\end{document}