\documentclass{article}
\usepackage[utf8]{inputenc}

\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{geometry}
\usepackage{multicol}

\geometry{
    left=1cm,right=1cm,top=2cm,bottom=2cm
}
\newcommand*\diff{\mathop{}\!\mathrm{d}}

\newtheorem{definition}{Определение}
\newtheorem{theorem}{Теорема}

\DeclareMathOperator{\sign}{sign}

\usepackage{hyperref}
\hypersetup{
    colorlinks, citecolor=black, filecolor=black, linkcolor=black, urlcolor=black
}

\title{Английский язык}
\author{Лисид Лаконский}
\date{October 2023}

\begin{document}
\raggedright

\maketitle

\tableofcontents
\pagebreak

\section{Практическое занятие — 28.10.2023}

\subsection{Intellectual Property: Software Protection, Resume}

\paragraph{Introduction}

\textbf{The article is about} intellectual property rights in the context of software.

\textbf{The author talks about} four types of intellectual property rights relevant to software: patents, copyrights, trade secrets and trademarks, the areas of applicability of each of them and the differences beetween them.

\paragraph{Main Content}

\textbf{According to the article}, a patent is a twenty years exclusive monopoly on the right to make, use and sell an invention which can protect features of a program that cannot be protected by other means. For example, ideas, methods, algorithms.

\textbf{Next, the author talks about a copyright and how it differs from a patent}. While a patent can protect the novel ideas, a copyright cannot. Copyright is intended to protect only the original expression of an idea. In the case of software, copyright law could protect the source and object code. Unlike a patent, copyright protection arises automatically upon the creation of a creative work.

\textbf{Finally, the author talks about trade secrets and trademarks}. A trade secret is an intellectual property that has inherent economic value because it is not known by others, and which the owner takes measures to keep secret. When it comes to software, the code and ideas expressed in it may be protected as trade secrets. This protection lasts as long as the protected element retains its trade secret status.

\textbf{Unlike the other intellectual property rights}, trademarks do not protect product, but the names or symbols that identifies product from a particular source and distinguishes it from others.

\paragraph{Conclusion}

\textbf{The author concludes} that in order to protect and obtain maximum benefit from a software asset, it is critical to have a good understanding of the intellectual property rights and how best to use the available forms of legal protection to protect those rights.

\end{document}